\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-29 syntax.tex

% Example : how judgemental equality is used for the universe
We review the concept of ``universe'' and at the same time showing how equality is representing semantic. In dependent type setting, function now can return type, of which the type is ``type of type'', i.e., \textit{the universe} $\cU$. We follow the style of \textit{name=ty/universe à la Tarski}~\cite{hofmann1997syntax} and
distinguish types from their \textit{codes or names} as showin in \ruleref{Code/Get Type}: given a \textit{code} (term) $\goodTerm{\Gamma}{T}{\cU}$ we can retrieve the corresponding type
$\goodType{\Gamma}{El~T}{}$, and vice-versa.\YZ{Why is it wanted to distinguish types from their codes?}

>>>>

% Example : how judgemental equality is used for the universe
We review the concept of ``universe'' and at the same time showing how equality is representing semantic. In dependent type setting, function now can return type, of which the type is ``type of type'', i.e., \textit{the universe} $\cU$. We follow the style of \textit{name=ty/universe à la Tarski}~\cite{hofmann1997syntax} and
distinguish types from their \textit{codes or names} as showin in \ruleref{Code/Get Type}: given a \textit{code} (term) $\goodTerm{\Gamma}{T}{\cU}$ we can retrieve the corresponding type
$\goodType{\Gamma}{El~T}{}$, and vice-versa.\YZ{Why is it wanted to distinguish types from their codes?}\EDJreply{Because in formalization, for a judgement $G |- t : T$, code can only be placed at $t$ and type can only be placed at $T$. In Russel style, they don't do such distinction. But for the sake of formalization, we will distinguish code and types.}
